Partial MILP to improve $\alpha,\beta$-CROWN accuracy \\ for hard DNN verification instances

### 2024-09-16 ICLR25/tables.tex
update tables.tex

\begin{tabular}{|c|c|c|c|c|c|}
	\hline
	Network & Accuracy & Upper bound & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s  \\ \hline
	MNIST 6$\times$100 &  & 90 & 33 & 35 & 40   \\ \hline
	MNIST 6$\times$200 &   & 96  & 46  & 49  & 50   \\ \hline
	MNIST 9$\times$100 &   & 86  & 23  & 28  & 28   \\ \hline
	MNIST 9$\times$200 &   & 91  & 35  & 36  & 37   \\ \hline
	MNIST 6$\times$500 &   & 94  & 41  & 43  & 44   \\ \hline
	CIFAR CNN-B-adv &   & 62  &   & 40  & 42   \\ \hline
	0 & 0 & 0 & 0 & 0 & 0  \\ \hline
\end{tabular}

\vspace*{4ex}
\begin{tabular}{|c|c|c|}
	\hline
	Verifier & Rate & Average time \\ \hline
	Marabou & 0 & 0 \\ \hline
	$\alpha,\beta$-Crown & 0 & 0 \\ \hline
	Full MILP & 0 & 0 \\ \hline
	0 & 0 & 0 \\ \hline
\end{tabular}

@@

\begin{tabular}{|c|c|c|c|c|c|}
	\hline
	Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ \hline
	& Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s) & Rate(\%) \hfill Time(s)\\ \hline
	MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & Rate \hfill Time \\ \hline
	MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & Rate \hfill Time \\ \hline
	MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & Rate \hfill Time \\ \hline
	MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & Rate \hfill Time \\ \hline
	0 & 0 & 0 & 0 & 0 & 0 \\ \hline
\end{tabular}

>>>>

\begin{table}
	\centering
	\caption{$\alpha,\beta$-Crown with pure BaB}
	\label{table_beta}
	\begin{tabular}{||c|c|c||c|c|c||}
		\hline
		Network & Acc & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline

		MNIST 6$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026.1s  \\  \hline
		MNIST 6$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930.3s  \\  \hline
		MNIST 9$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930.3s  \\  \hline
		MNIST 9$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083.1s  \\  \hline
		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1002.5s  \\  \hline
		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
	\end{tabular}
\end{table}

The following table is the summary of running results of some complete verifier with timeout = 10000s.

\begin{table}
	\centering
	\caption{SAME FORMAT for complete verifiers!!!}
	\label{table_complete}
	\begin{tabular}{||c||c|c|c||}
		\hline
		Network &  Marabou  & Full MILP & NNenum? \\ \hline
		MNIST 6$\times$100 & 26\% & 30\% & ?\%   \\ \hline
		$\epsilon = 0.026$ & 6520s & 7000s
		&  ?s  \\  \hline
	\end{tabular}
\end{table}

@@

\begin{table}
	\centering
	\caption{Gap between verified and attackable images. Lower is better}
	\label{table_undecided}
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Network & $\alpha,\beta$-Crown, 10s & $\alpha,\beta$-Crown, 30s & $\alpha,\beta$-Crown, 2000s & $\alpha,\beta$-Crown-refine & Our method \\ 
		& Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s) & Gap(\%) \hfill Time(s)\\ \hline
		MNIST 6$\times$100 & 57 \hfill 6.9 & 55 \hfill 18.9 & 50 \hfill 1026.1 & 13 \hfill 91.7 & 13 \hfill 46 \\ \hline
		MNIST 6$\times$200 & 50 \hfill 6.5 & 47 \hfill 16.6 & 46 \hfill 930.3 & 9 \hfill 79.8 & 8 \hfill 71 \\ \hline
		MNIST 9$\times$100 & 63 \hfill 7.2 & 58 \hfill 20.1 & 58 \hfill 1162.9 & 21 \hfill 102.2 & 15 \hfill 61 \\ \hline
		MNIST 9$\times$200 & 56 \hfill 6.8 & 55 \hfill 18.2 & 54 \hfill 1083.1 & 16 \hfill 83.2 & 8 \hfill 78 \\ \hline
		MNIST 6$\times$500 & 53 \hfill 6.4 & 51 \hfill 16.4 & 50 \hfill 1002.5 & (cannot run) & 10 \hfill 402 \\ \hline
		CIFAR CNN-B-adv & 28 \hfill 4.3 & 22 \hfill 8.7 & 20 \hfill 373 & N/A & 11 \hfill 417 \\ \hline
	\end{tabular}
\end{table}
